---
title: "Solving linear equation"
author: "Muhammad Reza Fahlevi"
output: html_notebook
---
Suppose that we have linear equation such that
$$
\begin{align}
  2x + 4y + 5z = -3 && \\
  3x + 2y + z = 2 && \\
  4x + y + 3z = 1 \\
\end{align}
$$
We can describe this system of linear equation.

## Simultaneous Linear Equation Description
### Trasform into Matrix Form and Solve for x, y, and z
In order to write the equation into its matrix, we need to write down the vector first, then we write its matrix

```{r}
vector_x <- c(2, 3, 4)
vector_y <- c(4, 2, 1)
vector_z <- c(5, 1, 3)
vector_out <- c(-3, 2, 1)

#Write the linear equation in the term of data frame
some_labels <- c('x_lands', 'y_lands', 'z_lands', 'output')
datum <- list(vector_x, vector_y, vector_z, vector_out)
names(datum) <- some_labels
data_frame <- data.frame(datum)
print(data_frame)
#Create the matrix
matrix_A <- matrix(cbind(vector_x, vector_y, vector_z), nrow=3, ncol=3, byrow=FALSE)
```
This is matrix A and its $det(A)$
```{r}
print(matrix_A)
cat("The determinant :", det(matrix_A))
```
And this is the invers of matrix A, $A^{-1}$ and its $det(A^{-1})$: 
```{r}
invers_matrix_A <- solve(matrix_A)
print(invers_matrix_A)
cat("The determinant :", det(invers_matrix_A))
```

We can find the value ($x,y,z$) using equation $$\textbf{x}=A^{-1} \textbf{y}$$
```{r}
X <- solve(matrix_A)%*%vector_out
X_data_frame <- data.frame(x_value=X[1], y_value=X[2], z_value=X[3])
print(X_data_frame)
```
### Eigen-Value, Eigen-Vector, and Diagonalisation
We can find the eigen-value of matrices using equation
$$
det(\lambda I - A) = 0
$$
By solving the characteristic-equation
$$
a_n \lambda^n + a_{n-1} \lambda^{n-1} + ... + a_0 \lambda^0 = 0
$$
The eigen-value of matrix A is {$\lambda_1, \lambda_2, ... , \lambda_n$}.
It can be done in R using function eigen.
```{r}
#Find eigen-value and eigen-vector of matrix A and its determinant
print(eigen(matrix_A))
print(paste0("The determinant :", det(eigen(matrix_A)$vectors)))


#Find the invers of eigen-vectors and its determinant
print(solve(eigen(matrix_A)$vectors))
print(paste0("The determinant :", det(eigen(solve(matrix_A))$vectors)))
```
The diagonalisation of matrix A is defined as
$$
V^{-1} A V
$$
Where V is defined as its eigen-vector of matrix A
```{r}
matrix_A_diagonal <- solve(eigen(matrix_A)$vectors)%*%matrix_A%*%eigen(matrix_A)$vectors
print(diag(diag(matrix_A_diagonal)))
```

