---
title: "Exercise in the end of Chapter-1"
output: html_notebook
---

This notebook discuss about the solution for exercise appear in book $Walpole, Myers, Myers, Ye. \textit{Probability & Statistics for Engineers & Scientist Eigth Edition. } Pearson.$

### Some Important Equation
#### Sample Mean
$$\bar x = \sum_{i = 0}^{n} \frac{x_i}{n} = \frac{x_1 + x_2 + ... + x_n}{n}$$
In this case, $x\in{N}$.

#### Median Value
$$
\widetilde x = \begin{cases} x_{ \frac{n+1}{2}} && \text{if n is odd} \\ \frac{1}{2} (x_{ \frac{x}{2}} + x_{ \frac{n}{2} + 1}) && \text{if n is even} \end{cases}
$$

#### Sample Variance
$$
s^2 = \sum_{i = 0}^{n} \frac{(x_i - \bar x)^2}{n-1}
$$

#### Standard Deviation
$$
\begin{align}
s & = \sqrt{s^2}\\
s & = \sqrt{\sum_{i = 1}^{n} \frac{(x_i - \bar x)^2}{n-1}}
\end{align}
$$

## Exercise 1.13
```{r}
#Assign the datum
the_data <- c(123, 116, 122, 110, 175, 126, 125, 111, 118, 117)
print(the_data)
print(length(the_data))   #print the size of data
print(mean(the_data))     #print the mean of data
print(median(the_data))   #print the median of data
```

## Exercise 1.14
```{r}
the_st_data <- c(572, 572, 573, 568, 569, 575, 565, 570)
print(the_st_data)    #display the data
print(length(the_st_data))  #print the size of data
print(mean(the_st_data))    #print the mean of data
print(median(the_st_data))  #print the median of data
print(var(the_st_data))     #print the variance of data
print(sqrt(var(the_st_data)))     #print the standard deviation
```

## Exercise 1.17
```{r}
Smokers <- Smokers[1:15]
print(Smokers)
print(length(Smokers) == length(Nonsmokers))
Smokers <- c(69.3, 56.0, 22.1, 47.6, 53.2, 48.1, 52.7, 34.4, 60.2, 43.8, 23.2, 13.8)
Nonsmokers <- c(28.6, 25.1, 26.4, 34.9, 29.8, 28.4, 38.5, 30.2, 30.6, 31.8, 41.6, 21.1, 36.0, 37.9, 13.9)
print(Smokers)    #print the Smokers
print(Nonsmokers) #print the Nonsmokers
print(length(Smokers)) #print the size of Smokers
print(length(Nonsmokers)) #print the size of Nonsmokers

smokers_nonsmokers <- cbind(summary(Smokers), summary(Nonsmokers))
smokers_nonsmokers <- data.frame(smokers = smokers_nonsmokers[,1], nonsmokers = smokers_nonsmokers[,2])
print(smokers_nonsmokers)   #The summary display in data frame
```

```{r}
for (i in 1:length(Smokers)) {
  print(Smokers[i] > Nonsmokers[i])
}
```

##### Display the data
```{r}
cat("Smokers : ", print(Smokers))
print("")
cat("Size of sample :", length(Smokers))
print("")
print(summary(Smokers))
print(fivenum(Smokers))
stem(Smokers)

#Visualisation the data using histogram
hist(Smokers)
hist(Smokers, seq(13.80, 69.4, 0.2), prob=TRUE)
line(density(Smokers, bw=0.1))
rug(Smokers)
boxplot(Smokers, Nonsmokers, col = "blue")
```
#### Conclusion
The smokers take more time to fall asleep then those who Nonsmokers

## Exercueses 1.18
```{r}
print(final_exam)
summary(final_exam)
print(var(final_exam)) #print the variance of the sample
print(sqrt(var(final_exam))) #print the standard deviation of sample
fivenum(final_exam)
stem(final_exam, scale=1, width = 80)
boxplot(final_exam, col="blue")
#To make sure that the stem-leaf is correct
#for (i in 1:length(final_exam)) {
#  if(final_exam[i] > 20 && final_exam[i] < 30) print(final_exam[i])
#}
```
### Display the data
```{r}
library(lattice)
hist(final_exam, 20, col="blue")
hist(final_exam, seq(10.0, 99.0, 0.2), prob=TRUE, col="blue")
lines(density(final_exam, bw=0.1))
rug(final_exam)
densityplot(final_exam)
qqmath(final_exam)
boxplot(final_exam)
```

