---
title: "Understanding read.tables Function in R"
author: "Muhammad Reza Fahlevi"
output:
  html_notebook: default
---
In this notebook, we will learn how to use read.tables function in order to read some data. In this case, I'll scrape it some data external using python code and read the data using R.

## A. Creating a WebScraping Class
In this notebook, I use the data from some url. But, before we can scrape some data in that url, we need to create a webscraping class with getUrl method using python.

```{r}
#Use reticulate package
library("reticulate")
use_python("/usr/bin/python", required = T)
#Bringing python3 to R

#py_urllib_request <- import("urllib.request")
#py_bs4 <- import("bs4")
#html <- py_urllib_request$urlopen("https://stats.idre.ucla.edu/stat/data/test.txt")
#bs <- py_bs4$BeautifulSoup(html$read(), "html5lib")
#print(bs)

```
Prepare and set up the environment for web scraping
```{python}
#Set up the package for web scraping
from urllib.request import urlopen
from bs4 import BeautifulSoup
#Set up the package for exception handling
from urllib.error import HTTPError
from urllib.error import URLError

#Creating a class WebScraping with getUrl method
class WebScraping:
  def __init__(self, someUrl):
    self.someUrl = someUrl
  
  def getUrl(self):
    try:
      html = urlopen(self.someUrl)
    except HTTPError:
      print('The url is not available')
      print(HTTPError)
      return None
    try:
      bs = BeautifulSoup(html.read(), 'html5lib')
      theData = bs.body.get_text()
    except URLError:
      print("Maybe the server is not available for now")
      print(URLError)
      return None
    except AttributeError:
      print("Maybe the tag is not there")
      print(AttributeError)
      return None
    
    return theData
```
Now, we are ready to learn scan and read.tables function

## B. $scan$ function
Suppose that we have a data as below
```{python}
#Create the python object
pyObject = WebScraping('https://stats.idre.ucla.edu/stat/data/scan.txt')
```
```{python}
print("Tag was not there") if(pyObject.getUrl() == None) else print(pyObject.getUrl())
```
```{r}
#We can read the data using scan() as follows
some_data <- scan('https://stats.idre.ucla.edu/stat/data/scan.txt', what=list(age=0, names=""))
print(some_data)
```
## $read.tables$ function
Here, we are discuss about very reliable to read data into R
```{python}
stPyObject = WebScraping('https://stats.idre.ucla.edu/stat/data/test.txt')
print("Attribute was not found maybe") if(stPyObject.getUrl() == None) else print(stPyObject.getUrl())
```

```{r}
#In the data frame form
(st_example <- read.table("https://stats.idre.ucla.edu/stat/data/test.txt", header = TRUE))
(as.list(st_example))
```
### Exception Handling
Suppose that we are given a table where the element of its there exist an empty value. For example.
```{python}
ndPyObject = WebScraping("https://stats.idre.ucla.edu/stat/data/test_missing_comma.txt")
print("Attribute maybe not found") if(ndPyObject.getUrl == None) else print(ndPyObject.getUrl())
```
```{r}
(nd_example <- read.table("https://stats.idre.ucla.edu/stat/data/test_missing_comma.txt", header=TRUE, sep=","))
print(as.list(nd_example))
```

