---
title: "R Notebook"
output: html_notebook
---

In this notebook, I want to try do data proccessing. In this case, I use dataset from https://www.kaggle.com/pavanraj159/predicting-a-pulsar-star

we start from importing .csv files.
```{r}
pulsar_star <- read.csv(
  file = 'predicting-a-pulsar-star/pulsar_stars.csv',
  header = TRUE,
  sep = ','
  )
print(pulsar_star)
```
Split each column to its own vector.
```{r}
st_type <- c(pulsar_star$Mean.of.the.integrated.profile)
nd_type <- pulsar_star$Mean.of.the.integrated.profile

print(length(pulsar_star$Mean.of.the.integrated.profile))

mean_of_integrated_profile <- pulsar_star$Mean.of.the.integrated.profile
std_of_integrated_profile <- pulsar_star$Standard.deviation.of.the.integrated.profile
exc_kurt_of_integrated_profile <- pulsar_star$Excess.kurtosis.of.the.integrated.profile
skew_of_the_integrated_profile <- pulsar_star$Skewness.of.the.integrated.profile

mean_of_the_DM_SNR_curve <- pulsar_star$Mean.of.the.DM.SNR.curve
std_of_the_DM_SNR_curve <- pulsar_star$Standard.deviation.of.the.DM.SNR.curve
exc_of_the_DM_SNR_curve <- pulsar_star$Skewness.of.the.DM.SNR.curve
skew_of_the_DM_SNR_curve <- pulsar_star$Skewness.of.the.DM.SNR.curve

target_class <- pulsar_star$target_class
```
Assingn the property of integrated_profile and DM_SNR_curve into lst_of_intgrated_profile and lst_of_DM_SNR_curve
```{r}
data_frame_of_integrated_profile <- data.frame(Mean=mean_of_integrated_profile, Standard_Deviation=std_of_integrated_profile, Exces_Kurtosis=exc_kurt_of_integrated_profile, Skewness=skew_of_the_integrated_profile)

data_frame_of_DN_SNR_curve <- data.frame(Mean=mean_of_the_DM_SNR_curve, Standard_Deviation=std_of_the_DM_SNR_curve, Exces_Kurtosis=exc_of_the_DM_SNR_curve, Skewness=skew_of_the_DM_SNR_curve)

print(data_frame_of_integrated_profile)
print(data_frame_of_DN_SNR_curve)
```
Visualize the data using histogram
```{r}
hist(data_frame_of_integrated_profile[[1]], xlab='range', main='mean_of_integrated_profile', col='blue')
hist(data_frame_of_integrated_profile[[2]], xlab='range', main='Standard_Deviation_of_integrated_profile', col='blue')
hist(data_frame_of_integrated_profile[[3]], xlab='range', main='Exces_Kurtosis_of_integrated_profile', col='blue')
hist(data_frame_of_integrated_profile[[4]], xlab='range', main='Skewness_of_integrated_profile', col='blue')

hist(data_frame_of_DN_SNR_curve[[1]], xlab='range', main='mean_of_DN_SNR_curve', col='navy')
hist(data_frame_of_DN_SNR_curve[[2]], xlab='range', main='Standard_Deviation_of_DN_SNR_curve', col='navy')
hist(data_frame_of_DN_SNR_curve[[3]], xlab='range', main='Exces_Kurtosis_of_DN_SNR_curve', col='navy')
hist(data_frame_of_DN_SNR_curve[[4]], xlab='range', main='Skewness_of_DN_SNR_curve', col='navy')
```
Since we have 8 column, the number of arrangement for 8 object with 2 cells is equals to C(8,2) = 8!/(8-2)!2!
We need to plot this possibility arrengement using plot function
```{r}
plot(data_frame_of_DN_SNR_curve$Mean, data_frame_of_DN_SNR_curve$Standard_Deviation, pch='+', col='blue')
```
