---
title: "R Notebook"
output: html_notebook

---

```{r}
print("Bidoof")
```

Suppose, for example, we have a sample of 30 tax accountants from all the states and territories
of Australia 1 and their individual state of origin is specified by a character vector of state
mnemonics as

```{r}
state <- c("tas","qld","sa","sa","sa","vic","nt","act","qld","nsw","wa","nsw","nsw","vic","vic","vic","nsw","qld","qld","vic","nt", "wa", "wa","qld", "sa", "tas","nsw", "nsw", "wa","act")
print(length(state))
statef <- factor(state)
print(statef)
print(levels(statef))
```

To continue the previous example, suppose we have the incomes of the same tax accountants in
another vector (in suitably large units of money)

```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56,
61, 61, 61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46,
59, 46, 58, 43)
print(length(incomes))
print(incomes)

#To calculate the sample mean income for each state 
#we can now use the special function tapply()
incmeans <- tapply(incomes, statef, mean)
print(incmeans)
```

Objects satisfying the restrictions placed on the columns (components) of a data frame may be
used to form one using the function data.frame

```{r}
accountants <- data.frame(home=statef, loot=incomes, shot=incomes)
print(accountants)
print(accountants$home)
print(accountants$loot)
```

Reading some_datum.csv files

```{r}
library(readr)
some_datum <- read_csv('some_datum.csv')
print(some_datum)
View(some_datum)
```



Reading data from from files.
In this section, we will learn about how to manage an data/information
from some files {.xls, .csv, ... , etc}

```{r}
pulsar_star <- read.csv("predicting-a-pulsar-star/pulsar_stars.csv", header=TRUE, sep=",", nrows=500, colClasses = c(rep('double', 3), rep('NULL', 6)))
names(pulsar_star) <- c('mean(int_prof)', 'std(int_prof)', 'excKurt(int_prof)')
print(pulsar_star)

Mean.of.the.integrated.profile <- c(pulsar_star$`mean(int_prof)`)
Standard.deviation.of.the.integrated.profile <- c(pulsar_star$`std(int_prof)`)
Excess.kurtosis.of.the.integrated.profile <- c(pulsar_star$`excKurt(int_prof)`)

hist(Mean.of.the.integrated.profile, 50, col='blue')
hist(Standard.deviation.of.the.integrated.profile, 50, col='blue')
hist(Excess.kurtosis.of.the.integrated.profile, 50, col='blue')
```

