---
title: "Probability Distribution"
output: html_notebook

---
source: R-intro from CRAN

## R as a set of statistical tables
```{r}
#Reading the csv data
distribution_name <- read.csv("probability_distribution.csv", header=TRUE)
print(distribution_name)
```
## Examining the distribution of set of data
Given a (univariate) set of data we can examine its distribution in a large number of ways. The
simplest is to examine the numbers. Two slightly different summaries are given by summary and
fivenum and a display of the numbers by stem (a “stem and leaf” plot).
```{r}
print(faithful)
summary(eruptions)
fivenum(eruptions)
```
```{r}
stem(eruptions)
```
```{r}
#Plotting the histogram
hist(eruptions)
#Make the bins smaller, make a plot density
hist(eruptions, seq(1.6, 5.2, 0.2), prob=TRUE, col="whitesmoke")
lines(density(eruptions, bw=0.1, col="blue"))
rug(eruptions, col="navy")
```
```{r}
#Plotting empirical cumulative distribution function
plot(ecdf(eruptions), do.points=FALSE, verticals=TRUE, col="blue")
```
This distribution is obviously far from any standard distribution. How about the right-hand
mode, say eruptions of longer than 3 minutes? Let us fit a normal distribution and overlay the
fitted CDF.
```{r}
long <- eruptions[eruptions > 3]
plot(ecdf(long), do.points=FALSE, verticals=TRUE)
x <- seq(3, 5.4, 0.01)
lines(x, pnorm(x, mean=mean(long), sd=sqrt(var(long))), lty=3)
```
Quantile-quantile (Q-Q) plots can help us examine this more carefully.
```{r}
par(pty="s")
# arrange for a square figure region
qqnorm(long); qqline(long)
```

