---
title: "Solution Notebook for Exercise in Section 1.4."
author: "Muhammad Reza Fahlevi"
output: html_notebook
---
This notebook discuss about the solution for exercise appear in book $Walpole, Myers, Myers, Ye. \textit{Probability & Statistics for Engineers & Scientist Eigth Edition. } Pearson.$

### Some Important Equation
#### Sample Mean
$$\bar x = \sum_{i = 0}^{n} \frac{x_i}{n} = \frac{x_1 + x_2 + ... + x_n}{n}$$
In this case, $x\in{N}$.

#### Median Value
$$
\widetilde x = \begin{cases} x_{ \frac{n+1}{2}} && \text{if n is odd} \\ \frac{1}{2} (x_{ \frac{x}{2}} + x_{ \frac{n}{2} + 1}) && \text{if n is even} \end{cases}
$$

#### Sample Variance
$$
s^2 = \sum_{i = 0}^{n} \frac{(x_i - \bar x)^2}{n-1}
$$

#### Standard Deviation
$$
\begin{align}
s & = \sqrt{s^2}\\
s & = \sqrt{\sum_{i = 1}^{n} \frac{(x_i - \bar x)^2}{n-1}}
\end{align}
$$

### Exercise 1.1
The following measurements were recorded for the drying time, in hours, of a certain brand of latex paint.
$$
\begin{align}
3.4 && 2.5 && 4.8 && 2.9 && 3.6 \\
2.8 && 3.3 && 5.6 && 3.7 && 2.8 \\
4.8 && 4.0 && 5.2 && 3.0 && 4.8
\end{align}
$$
Assume that the measurements are a simple random sample.

(a). What is the sample size for the above sample?
```{r}
#Assing the data in vector form
measurements <- c(3.4, 2.5, 4.8, 2.9, 3.6, 2.8, 3.3, 5.6, 3.7, 2.8, 4.8, 4.0, 5.2, 3.0, 4.8)
print(sum(measurements))
print(matrix(measurements, nrow=3, ncol=5, byrow=TRUE))
print(length(measurements)) #sample size for the above sample
```

(b). Calculate the sample mean for this data.
```{r}
print(mean(measurements))
```

(c). Calculate the sample meadian.
```{r}
sorted_measurements <- sort(measurements)
print(sorted_measurements)
print(sorted_measurements[8])
print(median(measurements))
print(sorted_measurements[8] == median(measurements))

print(var(sorted_measurements))
print(sqrt(var(sorted_measurements)))
```

(d). Plot the data by way of a dot plot.
```{r}
print(table(measurements))
print(plot(table(measurements)))
```

(e). Compute the 20% trimmed mean for the above data set.

### Exercise 1.3
```{r}
#Insert the data
no_aging <- c(227, 222, 218, 217, 225, 218, 216, 229, 228, 221)
aging <- c(219, 214, 215, 211, 209, 218, 203, 204, 201, 205)
tensile_strength <- data.frame(No_Aging = no_aging, Aging = aging)

print(tensile_strength)
print(summary(tensile_strength))

print(var(aging))
print(sqrt(var(aging)))

print(var(no_aging))
print(sqrt(var(no_aging)))
```
(a). Do a dow plot of the data
```{r}
print(plot(table(no_aging)))
print(plot(table(aging)))
```
(c). Calculate the sample mean tensile strength of the two samples
```{r}
print(mean(no_aging))
print(mean(aging))
```
